\texttt{gwsnr}: A python package for efficient signal-to-noise calculation of gravitational-waves

### 2025-06-21 arxiv/paper.tex
mac

This procedure transforms a computationally intensive integration into a
simple, JIT-compiled table lookup and multiplication, enabling massive
performance gains for large-scale population studies.

@@

>>>>

This procedure transforms a computationally intensive integration into a
simple, JIT-compiled interpolation and multiplication, enabling massive
performance gains for large-scale population studies.

@@

\section{References}\label{references}
